Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
minor comment

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of the variants (right)}
		\label{fig:boxplot}
		\vspace{-0.2cm}

>>>>

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of
      the variants (right)\Mar{por favor, aumente o tamanho dos labels
      (nao consigo enxergar na impressao).}}
		\label{fig:boxplot}
		\vspace{-0.2cm}
